Symmetric Circuits for Rank Gates

### 2018-01-15 sections/background.tex
dec 7
January 15 Update

>>>>

\subsection{Group Theory}
--Include details on how to define a groupa action. Particularly a group action
as a homomorphism from $G$ to $\sym_X$

Let $X$ be a set and $G$ be a group acting on $X$. We let the stabiliser of $S
\subseteq X$ for $G$ be defined as $\stab_G(S) := \{ \sigma \in G : \forall x
\in S \, \sigma \cdot x = x \}$ and the orbit of $S$ for $G$ to be defined as
$\orb_G (S) := \{ T \subseteq X : \exists \sigma \in G \, \sigma \cdot S = T
\}$. If $S = \{x\}$, for some $x \in X$, we write $\stab_G (x)$ and $\orb_G(x)$
in order to abbreviate $\stab_G(\{x\})$ and $\orb_G(\{x\})$, respectively. In
the event that the choice of $G$ is obvious from context we omit the subscript.

We are often interested in the case where $G$ is the symmetric group $\sym_n$ on
$n$ elements. In this case we write $\stab_n(x)$ and $\orb_n(x)$ in order to
abbreviate $\stab_{\sym_n}(x)$ and $\orb_{\sym_n}(x)$, respectively.

We are also often interested in the case where $G$ is the stabiliser group for
set of elements, or single element, from $X$. For $S, T \subseteq X$, we write
$\stab_{S}(T)$ and $\orb_{S}(T)$ in order to abbreviate $\stab_{\stab(S)}(T)$
and $\orb_{\stab(S)}(T)$.

### 2018-01-15 sections/symmetric-circuits.tex
January 15 Update

% AD - rewrote the paragraph to reduce the use of subscripts and superscripts.
Let $\tau = (R, S, \nu)$ be a many-sorted vocabulary.
% with $R = \{R_1 \ldots, R_t\}$, $S = \{s_1, \ldots , s_p\}$, and $\nu(R_i) =
% (a^i_1, \ldots , a^i_{r_i)})$, where $r_i = \arty(R_i)$ and $a^i_q \in S$ for
% all $q \in [r_i]$.
Let $D := \biguplus_{s \in S} D_{s} = \{(s,d) : d \in D_s\}$, be a disjoint
union of non-empty sets, indexed by $S$. We call $D$ a \emph{$\tau$-universe}.
For each $P \in R$, let $P^D$ denote the trivial relation over the many-sorted
universe $D$, i.e.\ $P^D := D_{a_1} \times \ldots \times D_{a_{r}}$, where
$\nu(P) = (a_1, \ldots , a_{r)})$. Let the \emph{index defined by the pair
  $(\tau, D)$} be the set $\biguplus_{P\in R} P^{D}$. We use this set to index
the input to a Boolean function, as such we abuse notation and denote the index
defined by $(\tau, D)$ by $\ind(\tau, D)$. We call $\tau$ the vocabulary and $D$
the universe of $\ind(\tau, D)$.

% GW: move sorted permutations into the background section
For the remainder of this subsection we fix a vocabulary $\tau$ and a
many-sorted set $D=\biguplus_{s \in S} D_{s}$ and let $X := \ind (\tau, D)$. Let
$G \leq \sym_{X}$, and let $\sortsym_D := \prod_{s \in S} \sym_{D_{s}}$. We
call the elements of $\sortsym_D$ \emph{sorted permutations}. Note that
$\sortsym(D)$ can be identified with a subgroup of $\sym_X$. There is an obvious
action of $G$ on $X$. We can extend this to an action on the set of functions of
the form $f: X \rightarrow X$, for any set $H$, defined by $\sigma \cdot f(x) =
f(\sigma \cdot x)$ for all $x \in X$, $\sigma \in G$.

% If $H$ is surjective, we say that \emph{$f$ indexes $H$ by $X$} or \emph{$f$
% indexes $H$ by $\mathcal{D}$}.
We say that two functions $f, g : X \rightarrow H$ are \emph{$G$-equivalent} if
there exists $\sigma \in G$ such that $f = \sigma \cdot g$. We say $f$ and $g$
are \emph{isomorphism-equivalent} if they are $\sortsym(D)$-equivalent. We are
often interested in the case where $H = \{0,1\}$, i.e.\ $f : X \rightarrow
\{0,1\}$. In this case $f$ defines for each relation $R^D_i$ a subset of that
relation, and thus determines a $\tau$-structure over the universe $D$. We note
that two functions $f, g: X \rightarrow \{0,1\}$ are isomorphism-equivalent if,
and only if, the two $\tau$-structures they determine are isomorphic.

@@

Structured functions give us a general framework for indexing the input sequence
to a Boolean function and associating with that function an appropriate symmetry
condition. Let $F$ be a $(\tau, D)$-structured function. We say $F$ is
\emph{$G$-invariant} if it is constant on $G$-equivalent input vectors, i.e. for
all $G$-equivalent $\vec{x}, \vec{y} \in \{0,1\}^{X}$, $F(\vec{x}) =
F(\vec{y})$. We say $F$ is \emph{isomorphism-invariant} if it is $\sortsym
(D)$-invariant. Note that a structured function with vocabulary $\tau$ is
isomorphism-invariant if, and only if, it decides a property of
$\tau$-structures.

@@

Let $C_n = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\mathbb{B},
\tau)$-circuit. The $n$ is used to indicates that $C_n$ accepts structures of
size $n$. For a gate $g \in C_n$, we define the \emph{index} of $g$, denoted by
$\ind(g)$, as $\ind(\Sigma(g))$. We define the relation $W \subseteq G^2$ by
$W(h,g)$ if, and only if, $h \in \range(L(g))$. For each $g \in G$ we let
$W(\cdot, g) := \{h \in G : W(h,g)\}$, and let $W(g, \cdot) := \{h \in G :
W(g,h)\}$. We call $W(\cdot, g)$ the \emph{children} of $g$ and $W(g, \cdot)$
the \emph{parents} of $g$. We also abbreviate $W(g, \cdot)$ by $H_g$. We let the
vocabulary and universe of $g$ be the vocabulary and universe of $\Sigma(g)$,
respectively.

>>>>

% AD - rewrote the paragraph to reduce the use of subscripts and superscripts.
Let $\tau = (R, S, \nu)$ be a many-sorted vocabulary. Let $D := \biguplus_{s \in
  S} D_{s} = \{(s,d) : d \in D_s\}$, be a disjoint union of non-empty sets,
indexed by $S$. For $R_i \in R$ let $R^D_i$ denote the trivial relation over the
many-sorted universe $D$, i.e.\ $R^D_i := D_{a_1} \times \ldots \times
D_{a_{r}}$, where $\nu(R_i) = (a_1, \ldots , a_{r)})$. There is an obvious
interpretation of $\tau$ over $D$ given by assigning each sort symbol in $\tau$
in the obvious manner and each relation symbol in $\tau$ to the trivial relation
over $D$. We call this \emph{the structure defined by $(\tau, D)$}, and denote
it by $\str(\tau, D)$.

The idea is to use the tuples in the relations of this structure as an index
set, and with the automorphisms of this structure defining a group action. Let
the \emph{index defined by the pair $(\tau, D)$} be the set $\biguplus_{R_i\in
  R} R^{D}_i$. We often use this set to index the input to a Boolean function,
as such we abuse notation and denote the index defined by $(\tau, D)$ by
$\ind(\tau, D)$, and call $\tau$ the vocabulary and $D$ the universe of
$\ind(\tau, D)$.

% GW: move sorted permutations into the background section
For the remainder of this subsection we fix a vocabulary $\tau$ and a
many-sorted set $D := \biguplus_{s \in S} D_{s}$, and let $X := \ind (\tau, D)$
and $G \leq \sym_{X}$. There is an obvious action of $G$ on $X$. There is also
an obvious action of the automorphism group $\str(\tau, D)$ on $X$ (with
permutations in $\str(\tau, D)$ acting element-wise on tuples in $X$). We denote
this group by $\aut(\tau, D)$, and identify it with the subgroup of $\sym_X$
that acts equivalently on $X$.

We can extend the action of $G$ on $X$ to an action on the set of functions of
the form $f: X \rightarrow H$, for any set $H$, defined by $\sigma \cdot f(x) :=
f(\sigma \cdot x)$ for all $x \in X$, $\sigma \in G$.

% and let $\sortsym_D := \prod_{s \in S} \sym_{D_{s}}$. We call the elements of
% $\sortsym_D$ \emph{sorted permutations}. Note that $\sortsym(D)$ can be
% identified with a subgroup of $\sym_X$.

% If $H$ is surjective, we say that \emph{$f$ indexes $H$ by $X$} or \emph{$f$
% indexes $H$ by $\mathcal{D}$}.

We say that two functions $f: \ind(\tau, D) \rightarrow H$ and $g: \ind(\tau',
D') \rightarrow H$ are \emph{isomorphism-equivalent} if there exists an
isomorphism $\pi :\str(\tau, D) \rightarrow \str(\tau', D')$ such that $f (x) =
g (\pi (x))$ for all $x \in \str(\tau, D)$. It is easy to see that
isomorphism-equivalence is an equivalence relation.

We are often interested in the case where $X = \ind(\tau, D) = \ind(\tau', D')$.
We say that $f, g X \rightarrow H$ are \emph{$G$-equivalent} if there exists
$\sigma \in G$ such that $f = \sigma \cdot g$. We note that in this case $f$ and
$g$ are \emph{isomorphism-equivalent} if, and only if, they are $\aut(\tau,
G)$-equivalent.

In this paper we will often let the co-domain $H$ be the binary symbols
$\{0,1\}$, and so consider functions of the form $f : X \rightarrow \{0,1\}$. In
this case we may think of $f$ as defining for each relation $R^D_i$ a subset of
that relation, and thus determining a $\tau$-structure over the universe $D$. We
note that two functions $f, g: X \rightarrow \{0,1\}$ are isomorphism-equivalent
if, and only if, the two $\tau$-structures they determine are isomorphic.

@@

Structured functions give us a general framework for indexing the input sequence
to a Boolean function and associating with that function an appropriate symmetry
condition, or notion of equivalence. Let $F$ be a $(\tau, D)$-structured
function. We say $F$ is \emph{$G$-invariant} if it is constant on $G$-equivalent
input vectors, i.e. for all $G$-equivalent $\vec{x}, \vec{y} \in \{0,1\}^{X}$,
$F(\vec{x}) = F(\vec{y})$. We say $F$ is \emph{isomorphism-invariant} if it is
$\aut(\tau, D)$-invariant. Note that a structured function with vocabulary
$\tau$ is isomorphism-invariant if, and only if, it decides a property of
$\tau$-structures.

@@

Let $C_n = \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\mathbb{B},
\rho)$-circuit. The $n$ is used to indicates that $C_n$ accepts structures of
size $n$. For a gate $g \in C_n$, we define the \emph{index} of $g$, denoted by
$\ind(g)$, as $\ind(\Sigma(g))$. We define the relation $W \subseteq G^2$ by
$W(h,g)$ if, and only if, $h \in \range(L(g))$. For each $g \in G$ we let
$W(\cdot, g) := \{h \in G : W(h,g)\}$ and $W(g, \cdot) := \{h \in G : W(g,h)\}$.
We call the elements of $W(\cdot, g)$ the \emph{children} of $g$ and the
elements of $W(g, \cdot)$ the \emph{parents} of $g$. We also abbreviate $W(g,
\cdot)$ by $H_g$.

We let the vocabulary and universe of $g$ be the vocabulary and universe of
$\Sigma(g)$, respectively, and denote the vocabulary of $g$ by $\vocab{g}$ and
the universe by $\universe{g}$. We also let $\aut(g) := \aut(\tau, D)$ and
$\str(g) := \str(\tau, D)$.

### 2018-01-15 sections/translating-formulas-to-cicuits.tex
January 15 Update

\begin{lem}
  Let $C_n$ be a $(\mathbb{B}, \tau)$-circuit with unique labels of size $n$ and
  $\sigma \in \sym_n$. There is an algorithm takes as input a circuit $C_n$ and
  $\sigma \in \sym_n$ and outputs for each gate $g$ its image under the unique
  automorphism extending $\sigma$ (if it exists). This algorithm runs in time
  polynomial in the combined size of the input circuit and the encoding of the
  permutation.
  \label{lem:compute-automorphisms}
\end{lem}
\begin{proof}
  Suppose $C_n = \langle G, \Omega, \Sigma, \Lambda, L \rangle$. We build up the
  mapping $\pi$ extending $\sigma$ recursively. If at some point in the
  recursive construction we arrive at a point where no mapping for $g$ can be
  found we halt at that point and return that no automorphism exists.

@@

  Let $h$ be an internal gate in the circuit and assume we have defined $\pi
  (g)$ for every gate $g$ of height less than $h$. Let $h'$ be a gate in the
  circuit such that $\Sigma(h) = \Sigma (h')$, $\pi L(h)$ is isomorphism
  equivalent to $L(h')$ and, if $h$ is an output gate then $h'$ is an output
  gate such that $\sigma \Omega^{-1}(h) = \Omega^{-1}(h')$. Since $C_n$ has
  unique labels we have that $\pi L(h)$ is isomorphism equivalent to $L(h')$ if,
  and only if, $L(h')^{-1}\pi L(h)$ acts like an isomorphism. This can be
  determined easily. If no such $h'$ exists halt and output that there is no
  automorphism extending $\sigma$. We have from Lemma \ref{} that if $C_n$ has
  unique labels then there is at most one such $h'$.

@@

This result uses a proof very similar to the one for a similar result proved by
Anderson and Dawar~\cite{Anderson17D}.

\begin{lem}
  There is an algorithm that takes as input a circuit $C_n$ with unique labels
  and decides if $C_n$ is symmetric. If $C_n$ is symmetric outputs the orbits
  and coarsest supporting partitions of every gate. Moreover, this algorithm
  runs in time polynomial in the size of the input circuit.
  \label{lem:computing support}
\end{lem}

\begin{proof}
  Suppose $C_n = \langle G, \Omega, \Sigma, \Lambda, L \rangle$. Let $(u, v) \in
  \sym_n$ be a transposition. We may use Lemma \ref{lem:compute-automorphisms}
  to determine the unique automorphism $\pi_{(u,v)}$ extending $(u, v)$. It is
  easy to see that, since the set of transpositions generate $\sym_n$, for all
  $(u,v) \in \sym_n$ $\pi_{(u,v)}$ the automorphism $\pi_{(u,v)}$ exists if, and
  only if, $C_n$ is symmetric. We note that there are ${n}\choose{2}$
  transpositions. It follows that we may check in polynomial time if $C_n$ is
  symmetric. If $C_n$ is not symmetric we output that it is not symmetric and
  halt.

  Suppose then that $C_n$ is symmetric. For transposition $(u, v) \in \sym_n$,
  let $\mathcal{P}_{(u,v)} := \{\{u,v\}\}\bigcup_{w \in [n] \setminus
    \{u,v\}}\{\{w\}\}$ be a partition of $[n]$. We have that $\pi_{(u,v)}$ fixes
  $g$ if, and only if, $\mathcal{P}_{(u,v)}$ supports $g$. Since we can
  efficiently check if $\pi_{(u,v)}$ fixes $g$ it follows that we can
  effeciently check if $\mathcal{P}_{(u,v)}$ supports $g$. Let $\mathcal{P}$ be
  the result of combining the set consisting of those partitions
  $\mathcal{P}_{(u,v)}$ that support $g$ using $\mathcal{E}$. From Proposition
  \ref{prop:combining-supporting-patitions} we have that $\mathcal{P}$ supports
  $g$. Suppose that $\mathcal{P}$ is not the coarsest supporting partition of
  $g$. Then there exists a partition $\mathcal{P}'$ supporting $g$ such
  $\mathcal{P}' \preceq P$ and $\mathcal{P}' \neq \mathcal{P}$. But then there
  exists $P \in \mathcal{P}$ and $P' \in \mathcal{P}'$ such that $P \subsetneq
  P'$. But then there exists $a , b \in P'$ such that $a \not\in P$. It follows
  that the transposition $(a,b)$ fixes $\mathcal{P}'$ and so $\pi_{(a,b)}$ fixes
  $g$, but then, $\mathcal{P}_{(a,b)}$ supports $g$ and so, from the
  construction of $\mathcal{P}$, $\mathcal{P}$ is fixed by $(a,b)$. But
  $\mathcal{P}$ is not fixed by $(a,b)$, so we have a contradiction. We thus
  have that $\mathcal{P}$ is the coarsest supporting partition of $g$.

  It remains to compute the orbit of a gate $g$. Let $S_0 := \{g\}$ and for each
  $i \geq 0$ let $S_{i+1} := S_i \bigcup_{(u,v) \in \sym_n} \pi_{(u,v)}S_i$. Let
  $S$ be the least fixed point. It is easy to see that $S \subseteq \orb(g)$ as
  every gate in $S$ is equal to the action of some sequence of automorphisms
  (extending transpositions) acting on $g$. Moreover, since the set of all
  transpositions generates $\sym_n$, it follows that $\orb(g) \subseteq S$ and
  so $\orb(g) = S$.

  Given the polynomial bound on the number of transpositions, and the
  polynomial-time bound on the algorithm from Proposition
  \ref{prop:combining-supporting-partitions}, it is easy to see that the
  procedures described above can be implemented so as to run in time polynomial
  in the size of the input circuit.
\end{proof}

>>>>

\begin{lem}
  There is an algorithm takes as input a $(\mathbb{B}, \tau)$-circuit $C$ of
  order $n$ with unique labels and $\sigma \in \sym_n$ and outputs for each gate
  $g$ its image under the unique automorphism extending $\sigma$ (if it exists).
  This algorithm runs in time polynomial in the combined size of the input
  circuit and the encoding of the permutation.
  \label{lem:compute-automorphisms}
\end{lem}
\begin{proof}
  Suppose $C = \langle G, \Omega, \Sigma, \Lambda, L \rangle$. We build up the
  mapping $\pi$ extending $\sigma$ recursively. If at some point in the
  recursive construction we arrive at a point where no mapping for $g$ can be
  found we halt at that point and return that no automorphism exists.

@@

  Let $h$ be an internal gate in the circuit and assume we have defined $\pi
  (g)$ for every gate $g$ of height less than $h$. Let $h'$ be a gate in the
  circuit such that $\Sigma(h) = \Sigma (h')$, $\pi L(h)$ is isomorphism
  equivalent to $L(h')$ and, if $h$ is an output gate then $h'$ is an output
  gate such that $\sigma \Omega^{-1}(h) = \Omega^{-1}(h')$. Since $C$ has unique
  labels we have that $\pi L(h)$ is isomorphism equivalent to $L(h')$ if, and
  only if, $L(h')^{-1}\pi L(h)$ acts like an isomorphism. This can be determined
  easily. If no such $h'$ exists halt and output that there is no automorphism
  extending $\sigma$. We have from Lemma \ref{} that if $C$ has unique labels
  then there is at most one such $h'$.

@@

\begin{cor}
  There is an algorithm takes as input a $(\mathbb{B}, \tau)$-circuit $C$ of
  order $n$, $\sigma \in \sym_n$, $g$ a gate in $C$, and $a \in \universe{g}$
  and, if there exists an automorphism of $C$ extending $\sigma$ such that
  $\sigma in \stab(g)$, outputs image of $a$ under $\sigma$.
  \label{cor:compute-automorphisms-labels}
\end{cor}
\begin{proof}
  Let $C = \langle G, \Omega, \Sigma, \Lambda, L \rangle$. Use the algorithm
  from Lemma \ref{lem:compute-automorphisms} to check if $\sigma$ extends to an
  automorphism on $C$ and $\sigma \in \stab(g)$. If not, return that no such
  automorphism exists. We thus have that $C$ is symmetric. Let $h \in H_g$ and
  $\vec{a} := L(g)^{-1}(h)$ be such that $a \in \vec{a}$, and let $i$ be the
  index of $a$ in $\vec{a}$. Output $\sigma \cdot a := L(g)^{-1}(\sigma h)(i)$.
\end{proof}

% \begin{lem}
%   Let $C_n$ be a $(\mathbb{B}, \tau)$-circuit with unique labels of size $n$
%   and $\sigma \in \sym_n$. There is an algorithm takes as input a circuit
%   $C_n$ and $\sigma \in \sym_n$ and outputs for each gate $g$ its image under
%   the unique automorphism extending $\sigma$ (if it exists). This algorithm
%   runs in time polynomial in the combined size of the input circuit and the
%   encoding of the permutation.
%   \label{lem:compute-automorphisms}
% \end{lem}
% \begin{proof}
%   Suppose $C_n = \langle G, \Omega, \Sigma, \Lambda, L \rangle$. We build up
%   the mapping $\pi$ extending $\sigma$ recursively. If at some point in the
%   recursive construction we arrive at a point where no mapping for $g$ can be
%   found we halt at that point and return that no automorphism exists.

%   Let $h$ be any gate in the circuit. Suppose $h$ is an input gate. If $h$ is
%   a constant gate then let $\pi (h) = h'$. If $h$ is a relational gate such
%   that $R := \Sigma(h)$ and check if there exists $h'$ such that $\Sigma (h')
%   = R$ and $\sigma \Lambda_R(h) = \Lambda_R(h')$ and, if $h$ is an output gate
%   then $h'$ is an output gate such that $\sigma Omega^{-1}(h) =
%   \Omega^{-1}(h')$. If such a $h'$ does not exist halt and output that there
%   is no automorphism extending $\sigma$. We have from Lemma \ref{} that if
%   such an $h'$ exists it must be unique, and we set $\pi(h) = h'$.

%   Let $h$ be an internal gate in the circuit and assume we have defined $\pi
%   (g)$ for every gate $g$ of height less than $h$. Let $h'$ be a gate in the
%   circuit such that $\Sigma(h) = \Sigma (h')$, $\pi L(h)$ is isomorphism
%   equivalent to $L(h')$ and, if $h$ is an output gate then $h'$ is an output
%   gate such that $\sigma \Omega^{-1}(h) = \Omega^{-1}(h')$. Since $C_n$ has
%   unique labels we have that $\pi L(h)$ is isomorphism equivalent to $L(h')$
%   if, and only if, $L(h')^{-1}\pi L(h)$ acts like an isomorphism. This can be
%   determined easily. If no such $h'$ exists halt and output that there is no
%   automorphism extending $\sigma$. We have from Lemma \ref{} that if $C_n$ has
%   unique labels then there is at most one such $h'$.

%   This recursive approach can be implemented as an algorithm that runs in time
%   polynomial in the combined size of the inputs and outputs the required
%   automorphism if it exists.
% \end{proof}

This result uses a proof very similar to the one for a similar result proved by
Anderson and Dawar~\cite{AndersonD17}.

\begin{lem}
  \label{lem:computing-support-orbit}
  There is an algorithm that takes in a subset $S \subseteq [n]$ and $x \in X$,
  where $X$ is some finite set such that there is a group action of $\stab(S)$
  on $X$ computable in time polynomial in $n$ and $\vert X \vert$ and outputs
  $\orb_{\stab(S)} (x)$ and $\SP_{\stab(S)}(x)$. This algorithm runs in time
  polynomial in $\vert X \vert$ and $n$.
\end{lem}
\begin{proof}
  Let $(u, v) \in \sym_{[n] \setminus S}$ be a transposition. We note that
  $(u,v) \in \stab(S)$ and there are ${n - \vert S \vert}\choose{2}$ many such
  transpositions. For a transposition $(u, v) \in \sym_{[n] \setminus S}$, let
  \begin{align*}
    \mathcal{P}_{(u,v)} := \{ \{u,v\}\} \bigcup_{w \in [n] \setminus \{ u,v \}} \{ \{ w \} \}
  \end{align*}
  be a partition of $[n]$. Then $\mathcal{P}_{(u,v)}$ supports
  $\stab_{\stab(S)}(x)$ if, and only if, $(u,v) \cdot x = x$.

  Let $\mathcal{P}$ be the partition formed by applying $\mathcal{E}$ to all
  $\mathcal{P}_{(u,v)}$ such that $(u,v) \cdot x = x$ (which can be checked in
  time polynomial in $\vert X \vert + n$). From
  Proposition~\ref{prop:combining-supporting-patitions} we have that
  $\mathcal{P}$ supports $\stab_{\stab(S)}(x)$. Suppose that $\mathcal{P}$ is
  not the coarsest supporting partition of $\stab_{\stab(S)}(x)$. Then there
  exists a partition $\mathcal{P}'$ supporting $\stab_{\stab(S)}(x)$ such that
  $\mathcal{P}' \preceq P$ and $\mathcal{P}' \neq \mathcal{P}$. And so there
  exists $P \in \mathcal{P}$ and $P' \in \mathcal{P}'$ such that $P \subsetneq
  P'$. But then there exists $a , b \in P'$ such that $a \not\in P$. Note that
  $(a,b)$ fixes $\mathcal{P}'$ and, since $\mathcal{P}'$ supports
  $\stab_{\stab(S)}(x)$, it follows that $(a,b) \in \stab_{\stab(S)}(x)$ and $a
  \not\in S$ and $b \not\in S$. But then we have that $(a,b) \cdot x = x$, and
  so $\mathcal{P}_{(a,b)}$ supports $\stab_{\stab(S))}(x)$ and thus, from the
  construction of $\mathcal{P}$, $\mathcal{P}$ is fixed by $(a,b)$. But we
  selected $a$ and $b$ such that $\mathcal{P}$ is not fixed by $(a,b)$, and so
  we have a contradiction. We thus have that $\mathcal{P}$ is the coarsest
  supporting partition of $\stab_{\stab(S)}(x)$.

  It remains to compute $\orb_{\stab(S)}(x)$. Let $M_0 := \{x\}$ and for each $i
  \geq 0$ let $M_{i+1} := M_i \bigcup_{(u,v) \in \sym_{[n] \setminus S}} (u,v)
  \cdot M_i$. Let $M$ be the least fixed point. It is easy to see that $M
  \subseteq \orb_{\stab(S)}(x)$ as every element of $M$ is equal to the action
  of some finite sequence of transpositions acting on $x$. Moreover, if $y \in
  \orb_{\stab(S)}(x)$, then there exists $\pi \in \stab(S)$ such that $y = \pi
  \cdot x$. But then, since $\sym_{[n] \setminus S}$, is generated by the set of
  all transpositions in $\sym_{[n] \setminus S}$, it follows that $\pi$ can be
  written as a sequence of $t$ transpositions (for some $t \in nats$). Thus $y
  \in M_t \subseteq M$, and hence $\orb_{\stab(S)}(x) \subseteq M$ and so
  $\orb_{\consp(G)}(x) = $.

  Note that the set of all transpositions in $\sym_{[n] \setminus S}$ can be
  computed in time $\mathcal{O}(n^{2})$ and whether such a transposition fixes
  $x$ can be computed in time polynomial in $\vert X \vert + n$. Moreover, since
  it is easy to show that $\mathcal{E}$ can be computed in time polynomial in
  $n$, it follows that $\mathcal{P}$ (defined above) can be computed in
  $\mathcal{O} (n^{2} q(\vert X \vert + n))$, for some polynomial $q$.

  Furthermore, since, when computing the orbit, the least fixed point must be
  reached in fewer than $\vert X \vert$ iterations, and each iteration requires
  at most $\mathcal{O} (n^{2})$ applications of the group action, it follows
  that the procedure terminates in time $\mathcal{O}(\vert X \vert n^{2} q'
  (\vert X \vert + n))$, for some polynomial $q'$. The result follows.
\end{proof}

\begin{lem}
  There is an algorithm that takes in a circuit $C$ of order $n$ with unique
  labels and outputs if the circuit is symmetric. If it is symmetric then it
  outputs the orbit and coarsest supporting partition of every gate. This
  algorithm runs in time polynomial in the size of the circuit.
  \label{lem:computing-support-orbit-gate}
\end{lem}

\begin{proof}
  For each transposition $(u,v) \in \sym_n$ and each gate $g$ in $C$ use
  Lemma~\ref{lem:compute-automorphisms} to check if the image of $g$ under
  $(u,v)$ exists. If for any transposition and gate the algorithm returns that
  no image exists then output that the circuit is not symmetric.

  We note that if all gates have an image under all transpositions then, since
  $\sym_n$ is generated by the set of transpositions, we have that $C$ is
  symmetric.

  We have from Lemma~\ref{lem:compute-automorphisms} that computing the action
  of $\sym_n$ on the gates of $C$ can be done in time polynomial in the size of
  the circuit. For each $g$ in $C$ use the algorithm from
  Lemma~\ref{lem:computing-support-orbit} with $S := \emptyset$, $X := G$, and
  $x := g$, and output the results.

  Since there are ${{n}\choose{2}} \leq n^2$ transpositions in $\sym_n$, the
  initial symmetry check can be completed in time polynomial in the size of the
  circuit. Moreover, from Lemmas~\ref{lem:compute-automorphisms} and
  \ref{lem:computing-support-orbit}, and the fact that $\vert C \vert \geq n$
  and $\vert C \vert \geq \vert \universe{g} \vert$, we have that the rest of
  the algorithm also runs in time polynomial in the size of the circuit.
\end{proof}

\begin{lem}
  There is an algorithm that takes in a circuit $C$ of order $n$ with unique
  labels, a gate $g$ in $C$ with small support, and $a \in \universe{g}$, and
  outputs if the circuit is symmetric. If it is symmetric it outputs the orbit
  $\orb_{\vec{\consp(g)}} (a)$ and coarsest supporting partition
  $\SP_{\vec{\consp(g)}} (a)$. This algorithm runs in time polynomial in the
  size of the circuit.
  \label{lem:computing-support-orbit-index}
\end{lem}
\begin{proof}
  Use the algorithm from Lemma~\ref{lem:computing-support-orbit-gate} in order
  to compute the canonical support of $g$. If the algorithm returns that $C$ is
  not symmetric, output that $C$ is not symmetric.

  Use the algorithm from Lemma~\ref{lem:computing-support-orbit}, with $S :=
  \consp(g)$, $X := \universe{g}$ and $x:= a$, and output the results.

  Notice that, since $\vert \universe{g} \vert \leq \vert C \vert$ and $n \leq
  \vert C \vert$, this algorithm runs in polynomial time.
\end{proof}

% \begin{lem}
%   There is an algorithm that takes in a symmetric circuit $C$ of order $n$
%   with unique labels, a gate $g$ in $C$ and $a \in \universe{g}$, the orbit
%   $\orb_g (a)$ and coarsest supporting partition $\SP_g (a)$.
% \end{lem}
% \begin{proof}
%   Let $(u,v) \in \sym_n$ be a transposition. We can check if $(u,v) \in
%   \stab(g)$ using Lemma~\ref{lem:compute-automorphisms}. Then $(u,v)$ acts
%   like an isomorphism at $g$, and hence $(u,v) \cdot a = L(g)^{-1}((\sigma
%   L(g)(\vec{x}))) (i)$, where $\vec{x} \in \ind(g)$ such that $\vec{x} (i) =
%   a$ for some $i \in [\vert \vec{x} \vert]$. Thus, since
%   Lemma~\ref{lem:compute-automorphisms} gives us that that we can compute
%   $\sigma L(g)(\vec{x})$ in polynomial time, we can compute $(u,v) \cdot a$ in
%   polynomial-time.

%   We note that

%   and hence we can compute $\sigma \cdot a$ effeciently. and hence compute
%   $\orb_g(a) = \{ \sigma \cdot a : \sigma \in \stab(g)\}$.
